---
title: "Actual vs Probable Cases"
description: |
  To analyze the accuracy of four states
author:
  - name: Sai Gottemukkula 
date: "`r Sys.Date()`"
output: distill::distill_article
bibliography: bibliography2.bib

---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(tidyverse)
library(rvest)
library(ggthemes)
library(janitor)
library(dplyr)
```

```{r conversion, echo = FALSE}
table <- read_csv(file = "United_States_COVID-19_Cases_and_Deaths_by_State_over_Time.csv", show_col_types = FALSE)
```

Something that I rarely see explored in the context of COVID-19 is how prediction models and AI are used to predict the number of probable cases. The results that I got were quite surprising!

```{r graphing, echo = FALSE}
table |>
  filter (state %in% c("CA", "MA", "WY", "MI"), submission_date == "12/25/2021") |>
  select(state, conf_cases) |>
  ggplot(aes(x = state, y = conf_cases, fill = state)) +
  geom_col() +
  labs(title = "Total Confirmed Cases For Four States", x = "States", y = "Cases (Scientific Notation)", subtitle = "Wyoming has the least cases", caption = "Source: CDC")
```

The graph above shows the *confirmed* cases for four different states.

```{r}
table |>
  filter (state %in% c("CA", "MA", "WY", "MI"), submission_date == "12/25/2021") |>
  select(state, prob_cases) |>
  ggplot(aes(x = state, y = prob_cases, fill = state)) +
  geom_col() +
  labs(title = "Total Probable Cases For Four States", x = "States", y = "Cases (Scientific Notation)", subtitle = "Wyoming has the least cases", caption = "Source: CDC")
```

Here, the graph shows the *probable* cases for the sames states, on the same day.

## Analysis
As you can see, the graphs show that the probable cases aren't exactly very accurate. In fact, they're off by thousands of cases! This shows that our predictions can use some improvements.

[@Source2]
