---
title: "Coronavirus Deaths vs Cases"
description: |
  To compare the deaths/cases ratio of the most left and right-leaning states.
author:
  - name: Sai Gottemukkula
    
date: "`r Sys.Date()`"
output: distill::distill_article
bibliography: bibliography2.bib

---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(tidyverse)
library(rvest)
library(ggthemes)
library(janitor)
library(dplyr)
```

```{r graph, echo = FALSE}
table <- read_csv(file = "United_States_COVID-19_Cases_and_Deaths_by_State_over_Time.csv", show_col_types = FALSE)
```

```{r conversion, echo = FALSE}
#colnames(table) = c("submission_date", "state", "tot_cases", "ChangeInTotalPercent")

table$tot_death <- as.numeric(table$tot_death)
table$tot_cases <- as.numeric(table$tot_cases)
```

For the first graphs, I'll compare the most left-leaning state's performance to that of the most right-leaning one during the beginning of the pandemic. According to worldpopulationreview, Hawaii is the most blue state, and Wyoming is the most red state. I'll use those for my comparison.

```{r graphing, echo = FALSE}
table |>
  filter(state == "HI") |>
  select(tot_cases, tot_death) |>
  ggplot(aes(x = tot_cases, y = tot_death)) +
  coord_cartesian(xlim = c(0, 100000), ylim = c(0, 1250)) +
  geom_point(size = 0.15) + 
  geom_smooth() +
  labs(title = "Coronavirus Cases To Deaths Ratio (Hawaii)", subtitle = "The line curves downwards", x = "Coronavirus Cases", y = "Coronavirus Deaths", caption = "Source: CDC")
```

The graph shows that Hawaii's cases have started to peak, and are curving downwards...

```{r}
table |>
  filter(state == "WY") |>
  select(tot_cases, tot_death) |>
  ggplot(aes(x = tot_cases, y = tot_death)) +
  coord_cartesian(xlim = c(0, 100000), ylim = c(0, 1250)) +
  geom_point(size = 0.15) + 
  geom_smooth() +
  labs(title = "Coronavirus Cases To Deaths Ratio (Wyoming)", subtitle = "The line curves up", x = "Coronavirus Cases", y = "Coronavirus Deaths", caption = "Source: CDC")
```

Here, you can see that the line curves upwards, and shows that the cases for Wyoming are increasing...

## Analysis
The two graphs show that Hawaii did slightly better than Wyoming at the start of the pandemic, as it had less deaths with the same amount of cases as Wyoming.


[@Source2]